\section{Introduction}

Environmental monitoring systems increasingly rely on distributed sensing infrastructures to collect observations about air quality, water quality, meteorological conditions, and other environmental parameters. Such data support public health assessment, environmental policy, infrastructure planning, agricultural decisions, and local risk management. \texttt{TODO:CITATION\_NEEDED} From an information-systems perspective, however, the reliability of environmental data depends not only on sensor accuracy, but also on the integrity of the complete data lifecycle: acquisition, transmission, storage, correction, aggregation, publication, and reuse.

Environmental sensor networks introduce several data integrity challenges. Measurements may be collected by geographically dispersed devices, transmitted through intermittent communication links, buffered locally before synchronization, processed by different organizations, or integrated into public and semi-public datasets. \texttt{TODO:CITATION\_NEEDED} These conditions are common in distributed monitoring settings, including but not limited to rural deployments, multi-station public networks, and heterogeneous monitoring infrastructures. Under such conditions, it may be difficult to determine whether a measurement record is original, complete, delayed, corrected, replayed, removed, or modified after collection.

The trustworthiness of environmental data therefore requires more than conventional storage. It requires provenance information that describes where a record originated, which sensor or gateway produced it, when it was collected, which transformations or corrections were applied, and who or what system authorized those changes. \texttt{TODO:CITATION\_NEEDED} Without such provenance, downstream users may be unable to distinguish between valid corrections, technical failures, missing observations, and unauthorized manipulation. This problem is especially important when environmental data are used for regulatory reporting, infrastructure monitoring, scientific analysis, or public communication. \texttt{TODO:CITATION\_NEEDED}

Blockchain-inspired audit trails offer one possible approach to this problem. The relevant idea is not cryptocurrency, tokenization, or fully public consensus. Rather, the useful properties are append-only event recording, cryptographic linking of records, timestamped transactions, hash-based verification, and explicit representation of permissions and corrections. \texttt{TODO:CITATION\_NEEDED} A lightweight blockchain-inspired architecture can store raw environmental measurements off-chain while preserving hashes, audit events, provenance metadata, and verification evidence in an integrity layer. Such a design may support later detection of unauthorized modification without requiring every environmental dataset to be stored directly on-chain.

This direction is motivated by data integrity practices from regulated environments, including clinical research, laboratory systems, and other domains where records must remain attributable, legible, contemporaneous, original, accurate, complete, consistent, enduring, and available. \texttt{TODO:CITATION\_NEEDED} In these environments, audit trails, controlled corrections, source data verification, role-based authorization, and traceable data custody are treated as core components of trustworthy data management. Although environmental monitoring systems are governed by different technical and legal requirements, the underlying integrity problem is related: collected observations must remain verifiable across organizational, technical, and temporal boundaries.

The research gap addressed in this work is the lack of a clearly defined and experimentally testable integrity framework that compares conventional storage, audit trails, hash chains, and provenance-aware verification for distributed environmental monitoring records. Existing work on environmental sensor networks often focuses on sensing, communication, calibration, data quality, or analytics, while blockchain-oriented environmental systems often emphasize decentralization or transparency. \texttt{TODO:CITATION\_NEEDED} Less attention has been given to environmental data integrity as a threat-coverage problem involving source record identity, timestamped provenance, controlled correction, hash verification, permission changes, audit review, and data custody from collection to publication. \texttt{TODO:CITATION\_NEEDED}

The primary research question is:

\begin{quote}
How do increasingly expressive integrity models compare in their ability to detect and explain threats to distributed environmental monitoring records?
\end{quote}

To answer this question, the study pursues the following objectives:

\begin{enumerate}
    \item Define a threat model for distributed environmental monitoring records.
    \item Compare four integrity models: conventional storage, audit trail, audit trail with hash chain, and audit trail with hash chain plus provenance and permission reconstruction.
    \item Propose a lightweight blockchain-inspired architecture that separates raw environmental measurements from hashes, audit metadata, permission events, and verification records.
    \item Specify verification workflows for value modification, timestamp modification, record deletion, fake insertion, replay, broken provenance, unauthorized correction, revoked key usage, missing correction reasons, and delayed synchronization.
    \item Evaluate the models through a reproducible proof-of-concept using public environmental monitoring data and controlled tampering scenarios.
\end{enumerate}

The expected contribution of this paper is a reproducible information-systems evaluation of blockchain-inspired integrity mechanisms for distributed environmental monitoring data. The contribution is intentionally scoped: it does not claim that blockchain technology improves environmental outcomes directly, nor does it propose a production blockchain network. Instead, it examines how audit trails, hash chains, provenance metadata, and permission reconstruction affect the detectable threat coverage of environmental records whose trustworthiness may otherwise be difficult to establish.
